Augraphy: An Augmentation Pipeline API for Modern Document Images

### 2023-01-10 paper.tex
add new model training and results metrics and discussion

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
\renewcommand{\floatpagefraction}{.8}%
\begin{document}

@@

\begin{abstract}
We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks. A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy. The library is used to produce a derivative of the NoisyOffice dataset, with which a simple convolutional neural network is trained and evaluated; the results of this experiment are discussed, followed by a look forward to further anticipated work.
\end{abstract}

\section{Introduction and Motivation}
Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types.\\

Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths. However, collecting or otherwise determining a set of labels for training data is quite challenging.  In the case of text documents, most real-world dirty documents /can't/ come with clean ground-truths.\\

@@

The NoisyOffice dataset contains folded sheets, wrinkled sheets, coffee stains, and footprint noise. The features given by the wrinkle and fold distortions can be mimicked with some Gaussian noise applied at various points along a line, and the features created by the stains and footprints can be mimicked with dark regions and thin lines. With Augraphy, we expected that we could use the BadPhotoCopy augmentation and the strikethrough behavior from the Markup augmentation to add these features to the ground-truth data, so we executed the following pipeline:

\begin{lstlisting}
ink_phase = []
paper_phase = []
post_phase = [BadPhotoCopy(), Markup()]

AugraphyPipeline(ink_phase, paper_phase, post_phase)
\end{lstlisting}
\subsection{Training Regime}
We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\

@@

\begin{table}
\centering
\caption{Model training statistics}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Model & NoisyOffice & Augraphy\\
\hline
Average Loss & 0.0010 & 0.0014\\
Mean Average Error & 0.0150 & 0.0142\\
Validation Loss & 7.4609e-04 & 8.9985e-04\\
Validation Mean Average Error & 0.0122 & 0.0112\\
Training Time & 190ms/step & 218ms/step\\
\hline
\end{tabular}
\end{table}

@@

The models predicted cleaned versions of the validation images (\ref{fig4}), which were then compared to the groundtruth versions according to each metric. The average over all such results was taken and is displayed in Table 2.

\begin{table}
\centering
\caption{Model performance on NoisyOffice validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Model &  Metric & Average value\\
\hline
NoisyOffice & PSNR & 63.09152246942623\\
Augraphy & PSNR & 63.11842705899114\\
NoisyOffice & SSIM & 0.8726093605602885\\
Augraphy & SSIM & 0.8633782608031118\\
NoisyOffice & RMSE & 0.1878745854176291\\
Augraphy & RMSE & 0.1866188481559681\\
\hline
\end{tabular}
\end{table}

Despite the models having been trained to minimize the mean squared error, they performed quite well on the RMSE, SSIM, and PSNR tasks. RMSE is a general indicator of the model's denoising efficacy, while PSNR specifically looks at distributed noise features like Gaussian noise; structural-similarity is less useful in this case because we weren't concerned with superresolution or other tasks, but we include it as a baseline for future work.\\

@@

\subsection{Tuning Augraphy}
The Augraphy pipeline used to generate training data for the Augraphy model was extremely naive, and only contained two augmentations; no attempt was made to adjust the default settings, demonstrating Augraphy's high degree of both utility and ease-of-use. Much of the data used in training contained an excessive amount of added noise, making the image unreadable to the human eye, and too noisy to recover text features from. Producing the most accurate model with Augraphy requires careful fine-tuning of the augmentation input parameters.

\subsection{Additional Techniques}
For brevity of both page length and time, this article only includes experimental results for one type of model. We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion models, generative adversarial networks, and ensembles of these. During the validation task, the naive Augraphy model adequately removed the page fold and wrinkle noise, but considerably degraded the foreground text. By comparison, the NoisyOffice model left more of the text untouched, but allowed more of the stain features to remain. The Augraphy model's performance suggests that better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model.\\

Human toil is needed to assemble initial datasets. To alleviate this, we are developing another library for generating document images purely synthetically, and intend to release a library for that soon.

>>>>

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage[colorlinks]{hyperref}
\hypersetup{
    colorlinks = false,
    linkbordercolor = {blue}
}
\usepackage{listings}
\usepackage{courier}
\renewcommand{\floatpagefraction}{.8}
%
\begin{document}

@@

\begin{abstract}
We introduce Augraphy, a library for constructing feature augmentation pipelines for building modern document image datasets suitable for machine learning tasks. A discussion of prior art in the synthetic document image distortion space precedes description of the motivation for and structure of Augraphy. The library is used to quickly produce a derivative of the NoisyOffice dataset, on which a simple convolutional neural network is trained, which on some metrics outperforms the same network trained on the NoisyOffice set; the results of this experiment are discussed, followed by a look forward to further anticipated work.
\end{abstract}

\section{Introduction and Motivation}
Augraphy was created as a way to generate features that mimic those of real-world dirty documents, enabling users to produce datasets useful for training denoisers, layout classifiers, optical character recognizers, shadow and watermark removers, binarizers, deblurrers, defaders, layout classifiers, document image segmenters, and many other model types. Training supervised learning models requires labeled datasets, which contain pairs of training data objects and associated labels, or ground-truths. However, collecting or otherwise determining a set of labels for training data is quite challenging.  In the case of text documents, most real-world dirty documents /can't/ come with clean ground-truths.\\

@@

The NoisyOffice dataset contains folded sheets, wrinkled sheets, coffee stains, and footprint noise. The features given by the wrinkle and fold distortions can be mimicked by overlaying the foreground text on wrinkled and folded paper textures, as the NoisyOffice team did, and the features created by the stains and footprints can be mimicked by introducing dark regions and thin lines. With Augraphy, we expected that we could use the BadPhotoCopy augmentation to produce the dark regions and a combination of the strikethrough behavior from the Markup augmentation and the smooth curve shading behavior of the PencilScribbles augmentation to add the last feature to the ground-truth data. The PaperFactory augmentation makes the paper texture overlay trivial and repeatable. In the end, we executed the following pipeline:

\begin{lstlisting}
ink_phase = []
paper_phase = [PaperFactory(p=0.5)]
post_phase = [
  BadPhotoCopy(p=0.5),
  PencilScribbles(p=0.5),
  Markup(markup_color=(0,0,0), p=0.5)
]

AugraphyPipeline(ink_phase, paper_phase, post_phase)
\end{lstlisting}

In each of the augmentations created above, the probability of applying to the image passing through the pipeline was set to 50\%, and the strikethrough behavior (the default) for the Markup augmentation was set to strike out words with only black lines.\\

The PaperFactory augmentation reads and randomly crops image textures from a local directory; to this we added two \footnote{\url{https://p2.piqsels.com/preview/642/889/110/paper-crease-creased-texture.jpg
}}, \footnote{\url{https://blog.miklavcic.si/wp-content/uploads/2011/11/white_paper_1.png}} public domain images of wrinkled paper found on Bing.

\subsection{Training Regime}
We fit the model architecture described in the previous section to both the NoisyOffice corpus and a derivative work generated with Augraphy applied to the NoisyOffice ground truth images.\\

@@

@@

Over the last 5 epochs of training, the performance of the models on average loss, average mean-average-error (MAE), average validation loss, and average validation MAE were recorded. The models predicted cleaned versions of the validation images (Figure 4), which were then compared to the groundtruth versions according to each metric. The average over all such results obtained during validation was taken. These metrics are displayed in Table 1.

\begin{table}
\centering
\caption{Model training statistics and performance on NoisyOffice validation task}\label{tab1}
\begin{tabular}{|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|@{\hspace{2em}}l@{\qquad}|}
\hline
Metric & NoisyOffice & Augraphy\\
\hline
PSNR & 63.09152246942623 & 63.3491691640664\\
SSIM & 0.8726093605602885 & 0.8662918306486613\\
RMSE & 0.1878745854176291 & 0.18310202817380003\\
Test Loss & 0.0011 & 0.0012\\
Test MAE & 0.0150 & 0.0129\\
Validation Loss & 7.5551e-04 & 8.22202e-04\\
Validation MAE & 0.01236 & 0.01076\\
Training Time & 190ms/step & 218ms/step\\
\hline
\end{tabular}
\end{table}

The Augraphy model outperforms the PSNR score of the NoisyOffice model on the validation task by half a percent, and has a lower mean average error both in test and validation during training, but underperforms by 0.8\% on structural similarity and 2.5\% on RMSE in validation, with a higher average test and validation loss. These numbers are consistent with the visual prediction results displayed in Figure 1: the Augraphy model predicts fewer pixels in the text (RMSE lower by 2.5\%), but removes more noise and with a higher degree of fidelity than the NoisyOffice model (PSNR higher by 0.2576466946). The training metrics collected indicate that the Augraphy model has lower variance so is more precise than the NoisyOffice model, but exhibits higher loss and thus less accuracy in its predictions.

@@

\subsection{Tuning the Pipeline}
The pipeline used to generate training data for the Augraphy model was extremely naive, and only contained four augmentations, most with default parameters, demonstrating Augraphy's high degree of both utility and ease-of-use. However, much of the data used in training contained an excessive amount of added noise, making the image unreadable to the human eye, and too noisy to recover text features from. Producing the most accurate model with Augraphy requires careful fine-tuning of the augmentation input parameters to generate training images closer to the validation set.

\subsection{Additional Techniques}
For brevity, this article only includes experimental results for one type of model. We plan to evaluate denoisers built with other architectures, particularly transformers, diffusion and generative adversarial networks, and ensembles of these. During the validation task, the naive Augraphy model correctly removed the page fold and wrinkle noise, but visually degraded regions of the foreground text. By comparison, the NoisyOffice model left more of the text intact, but permitted more of the stain features to remain in the output. Better results may be achieved by a sequential model built from an Augraphy-trained denoiser followed by an inpainting model to repair the text.\\
